---
title: "GreenPerformance"
output: html_document
date: "2025-02-20"
---

#q: what does the code chunk below do?
#A: It loads the necessary libraries and the ESG data.

# Load libraries and data
```{r setup, include=FALSE}
repo_path = "/workspaces/BBM104"

library(tidyverse)
library(lubridate)
library(kableExtra)
load(file.path(repo_path, "/Session06/ESG_data.RData"))

```

#q: What does the selected code chunk do? Please summarize the logical flow intuitively without showing each line of code in your reply.

#A: The selected code chunk sets up the environment for the analysis. It defines the repository path, loads necessary libraries (tidyverse, lubridate, and kableExtra), and loads the ESG_data dataset from a specified file path. This setup ensures that all required tools and data are available for subsequent analysis in the document.



```{r}
q <- 0.5
ESG_data |> 
  filter(year(date) > 2002, year(date) < 2024) |>
  filter(source == "Provider_B") |>
  group_by(date) |>                # This means that all operations will be run date by date, separately
  mutate(type = if_else(esg_metric > quantile(esg_metric, q, na.rm = T), # This creates the sorts...
                        "Green",                                         # ...Green if high ESG...
                        "Brown")) |>                                     # ...Brown if not
  select(name, date, close, esg_metric, type)                            # Select a few columns

```

What does the selected code chunk do? Please summarize the logical flow intuitively without showing each line of code in your reply.


#A: The selected code chunk processes the ESG_data dataset to analyze firm performance based on ESG metrics. It filters the data to include records from 2003 to 2023 and only from "Provider_B". It groups the data by date and classifies firms into "Green" or "Brown" based on whether their ESG metric is above or below the median for that date. Finally, it selects relevant columns (name, date, close, esg_metric, and type) for further analysis.

#q: Based on your reply above, how should the heading of this chunk be called?
#A: Filtering and Classifying ESG Data by Date and Source

Classifying Firms Based on ESG Metrics



# Processing and Analyzing ESG Data for Firm Performance
```{r}
q <- 0.5
ESG_data |> 
  filter(year(date) > 2002, year(date) < 2024) |>
  filter(source == "Provider_B") |>
  group_by(date) |>                # This means that all operations will be run date by date, separately
  mutate(type = if_else(esg_metric > quantile(esg_metric, q, na.rm = T), # This creates the sorts...
                        "Green",                                         # ...Green if high ESG...
                        "Brown")) |>                                     # ...Brown if not
  ungroup() |>
  group_by(name) |>                                                      # Now we group by firm
  mutate(return = close / lag(close) - 1) |>                             # Here we compute the return
  filter(return < 3) |>                                                  # Remove crazy returns
  select(name, date, close, esg_metric, type, return)

```

#A: The selected code chunk processes the ESG_data dataset to analyze firm performance based on ESG metrics. It filters the data to include records from 2003 to 2023 and only from "Provider_B". It groups the data by date and classifies firms into "Green" or "Brown" based on whether their ESG metric is above or below the median for that date. After ungrouping, it groups the data by firm and calculates the stock return for each firm. It filters out extreme returns and selects relevant columns for further analysis.



```{r}
ESG_data <- ESG_data |>  
  group_by(name) |>                                           # Now we group by firm
  mutate(return = close / lag(close) - 1) |>                  # Here we compute the return             
  ungroup() 
```


```{r}
q <- 0.5
ESG_data |> 
  filter(year(date) > 2002, year(date) < 2024) |>
  filter(source == "Provider_B", is.finite(esg_metric)) |>    # Keeps non missing ESG fields
  group_by(date) |>                    # All operations will be run date by date, separately
  mutate(type = if_else(esg_metric > quantile(esg_metric, q), # This creates the sorts...
                        "Green",                              # ...Green if high ESG...
                        "Brown")) |>                          # ...Brown if not
  ungroup() |>
  filter(return < 3) |>                                       # Remove crazy returns
  group_by(type) |>
  summarise(avg_return = mean(return, na.rm = T))  |>
  kableExtra::kable(caption = 'ESG metric and portfolio performance (q = 0.5) - Provider B')
```


```{r}
q <- 0.5
ESG_data |> 
  filter(year(date) > 2002, year(date) < 2024) |>
  filter(source == "Provider_A", is.finite(esg_metric)) |>    # Keeps non missing ESG fields
  group_by(date) |>                    # All operations will be run date by date, separately
  mutate(type = if_else(esg_metric < quantile(esg_metric, q), # This creates the sorts...
                        "Green",                              # ...Green if high ESG...
                        "Brown")) |>                          # ...Brown if not
  ungroup() |>
  filter(return < 2) |>                                       # Remove crazy returns!
  group_by(type) |>
  summarise(avg_return = mean(return*12, na.rm = T)) |>
  kableExtra::kable(caption = 'ESG metric and portfolio performance (q = 0.5) - Provider A')
```


```{r}
q <- 0.5
ESG_data |> 
  filter(year(date) > 2002, year(date) < 2024) |>
  mutate(intensity = scope_3 / market_cap) |>
  filter(source == "Provider_A", is.finite(intensity)) |>     # Keeps non missing ESG fields
  group_by(date) |>                    # All operations will be run date by date, separately
  mutate(type = if_else(intensity < quantile(intensity, q),   # This creates the sorts...
                        "Green",                              # ...Green if high ESG...
                        "Brown")) |>                          # ...Brown if not
  ungroup() |>
  filter(return < 2) |>                                       # Remove crazy returns
  group_by(type) |>
  summarise(avg_return = mean(return*12, na.rm = T) * 12)  |>    # Annualize
  kableExtra::kable(caption = 'Scope 3 intensity and portfolio performance (q = 0.5)')
```


```{r}
q <- 0.2
ESG_data |> 
  filter(year(date) > 2002, year(date) < 2024) |>
  filter(source == "Provider_B") |>
  group_by(date) |>                # This means that all operations will be run date by date, separately
  mutate(type = if_else(esg_metric > quantile(esg_metric, 1-q, na.rm = T),  # This creates the sorts...
                        "Green",                                            # Green if high
                        if_else(esg_metric < quantile(esg_metric, q, na.rm = T),
                                "Brown",                                 # ...Brown if low...
                                "Grey"))) |>                             # ... Grey otherwise
  ungroup() |>
  filter(is.finite(esg_metric), return < 3) |>
  group_by(type) |>
  summarize(avg_return = mean(return*12, na.rm = T))  |>
  kableExtra::kable(caption = 'ESG metric and portfolio performance (q = 0.2)')
```

```{r}
q <- 0.2
ESG_data |> 
  filter(year(date) > 2002, year(date) < 2024) |>
  mutate(intensity = scope_3 / market_cap) |>
  filter(source == "Provider_A", is.finite(intensity)) |>     # Keeps non missing ESG fields
  group_by(date) |>                    # All operations will be run date by date, separately
  mutate(type = if_else(intensity < quantile(intensity, q),   # This creates the sorts...
                        "Green",                              # ...Green if high ESG...
                        if_else(intensity > quantile(intensity, 1-q),
                                "Brown",
                                "Grey"))) |>                          # ...Brown if not
  ungroup() |>
  group_by(name) |>                                           # Now we group by firm
  mutate(return = close / lag(close) - 1) |>                  # Here we compute the return             
  ungroup() |>
  filter(return < 2) |>
  group_by(type) |>
  summarise(avg_return = mean(return, na.rm = T) * 12) |>
  kableExtra::kable(caption = 'Scope 3 intensity and portfolio performance (q = 0.2)')
```

