---
title: "Setup to run once" 
output: html_document
date: "2025-02-20"
---

# Run the below once to install R (instructions from https://cran.r-project.org/bin/linux/ubuntu/)
# update indices
sudo apt update -qq
# install two helper packages we need
sudo apt install --no-install-recommends software-properties-common dirmngr
# add the signing key (by Michael Rutter) for these repos
# To verify key, run gpg --show-keys /etc/apt/trusted.gpg.d/cran_ubuntu_key.asc 
# Fingerprint: E298A3A825C0D65DFD57CBB651716619E084DAB9
wget -qO- https://cloud.r-project.org/bin/linux/ubuntu/marutter_pubkey.asc | sudo tee -a /etc/apt/trusted.gpg.d/cran_ubuntu_key.asc
# add the repo from CRAN -- lsb_release adjusts to 'noble' or 'jammy' or ... as needed
sudo add-apt-repository "deb https://cloud.r-project.org/bin/linux/ubuntu $(lsb_release -cs)-cran40/"
# install R itself
sudo apt install --no-install-recommends r-base
# Click 'extension' button on the left vertical bar of VS Code; search REditorSupport; install this extension
# To ensure R executable path is correctly set in your VS Code settings, 
#   click 'wheel' button on the left vertical bar of VS Code; select Settings;
#   search for r.rpath.linux; set it to the path of your R executable, e.g., "r.rpath.linux": "/usr/bin/R"


# Run commands in this chunk one by one (**only once**) to install radian Terminal and Jupyter (if you know how to use them)
```{r}

# Set PKG_CONFIG_PATH to ensure the compiler can find the FreeType headers
Sys.setenv(PKG_CONFIG_PATH = "/usr/local/lib/x86_64-linux-gnu/pkgconfig:/usr/local/lib/pkgconfig:/usr/local/share/pkgconfig:/usr/lib/x86_64-linux-gnu/pkgconfig:/usr/lib/pkgconfig:/usr/share/pkgconfig")
# Install radian Terminal
system("mkdir -p /workspaces/BBM104/Python_Library")
system("pip3 install -U radian --target /workspaces/BBM104/Python_Library")
# To install Jupyter and upgrade pip
#pip3 install -U Jupyter --target /workspaces/BBM104/Python_Library
#python3 -m pip install --upgrade pip
# To ensure that the directory is included in your PYTHONPATH permanently
#echo 'export PYTHONPATH=/workspaces/BBM104/Python_Library:$PYTHONPATH' >> ~/.bashrc
#source ~/.bashrc

```


# Run commands in this chunk one by one (**only once**) to set up the R environment
```{r setup, include=FALSE}

# Create the R_Library directory
system("mkdir -p /workspaces/BBM104/R_Library")

# Add the R-library directory to the search path (Run in R after R is installed but before any R library is installed)
.libPaths(c("/workspaces/BBM104/R_Library", .libPaths()))

install.packages('languageserver')

install.packages("remotes")
install.packages(c("xml2", "stringi", "vctrs"))
install.packages("rvest")
install.packages("magrittr")


install.packages("collections") #, lib="/workspaces/BBM104/R_Library")
install.packages("jsonlite")#, lib="/workspaces/BBM104/R_Library")
install.packages("fs")#, lib="/workspaces/BBM104/R_Library")
#  install.packages("purrr")#, lib="/workspaces/BBM104/R_Library")


install.packages("dplyr")
install.packages("tidyr")#, lib="/workspaces/BBM104/R_Library")
install.packages("ggplot2")

#install.packages(c("timechange", "lubridate"))
#install.packages("htmltools")
#install.packages("svglite")
#install.packages("kableExtra")
#install.packages(c("tidyverse", "kableExtra"), dependencies = TRUE)


# Do not include the dependencies=T flag
#/usr/bin/
#R --silent --slave --no-save --no-restore -e "install.packages('languageserver', repos='https://cloud.r-project.org/', lib='/workspaces/BBM104/R_Library')"
#packageVersion("languageserver")


#====================================================

# Install Ubuntu packages harfbuzz and libfribidi
# harfbuzz is primarily a text shaping library used for rendering text
# fribidi is a library that provides support for the Unicode Bidirectional Algorithm (Bidi)
system("sudo apt-get install -y libharfbuzz-dev")
system("sudo apt-get install -y libfribidi-dev")
system("sudo apt-get install -y libfreetype6-dev libpng-dev libtiff5-dev libjpeg-dev")
# To find the installed location
system("dpkg-query -L libharfbuzz-dev")
system("dpkg-query -L libfribidi-dev")
system("dpkg-query -L libfreetype6-dev libpng-dev libtiff5-dev libjpeg-dev")

```


# Run the below once to install the necessary packages
```{r}

# Load necessary libraries
library(rvest) 
library(magrittr) 

required_packages <- c()
tar_gz_files <- c()
exact_files <- c()
# Save the required packages into a vector of strings
required_packages <- c(#'vctrs', 
'cli', 'glue', #'stringi', 
'rlang', 'curl', 'mime', 'fansi', 'pkgconfig', 'sys',
'askpass', 'openssl', 'utf8', 'httr', 'selectr', 'purrr', #'xml2', 
'pillar', 'tibble'
                       )
# Collect the list of .tar.gz files from the webpage
url <- "https://cran.r-project.org/src/contrib/"
page <- rvest::read_html(url)
tar_gz_files <- page %>% rvest::html_nodes("a") %>% rvest::html_attr("href") %>% 
                grep("\\.tar\\.gz$", ., value = TRUE)

# Extract the exact full names of the .tar.gz files to be downloaded
exact_files <- tar_gz_files[grepl(paste0("^(", paste(required_packages, collapse = "|"), ")_.*\\.tar\\.gz$"), basename(tar_gz_files))]

# Start a loop over the list of exact full names of .tar.gz files to download all the files
for (file in exact_files) {
  #print(paste0(url, file))
  download.file(paste0(url, file), destfile = file)
}

# Use a vector-based syntax to install all the downloaded packages
install.packages(exact_files, repos = NULL, type = "source", dependencies = TRUE)
# Use remotes::install_local to install all the downloaded packages
#for (file in exact_files) {
#  remotes::install_local(file, dependencies = TRUE)
#}

```


# Run the below once to install more packages
```{r}

# Load necessary libraries
library(rvest) 
library(magrittr) 

required_packages <- c()
tar_gz_files <- c()
exact_files <- c()
# Save the required packages into a vector of strings
required_packages <- c("bit", "fastmap", "rappdirs", "uuid", "htmltools", "viridisLite", 
"colorspace", "xfun", "ps", "processx", "sass", "base64enc", 
                        "farver", "labeling", "munsell", "RColorBrewer", 
                        "rematch", "blob", "DBI", "gtable", "isoband", 
                       "rematch2", "prettyunits"
                       )
# Collect the list of .tar.gz files from the webpage
url <- "https://cran.r-project.org/src/contrib/"
page <- rvest::read_html(url)
tar_gz_files <- page %>% rvest::html_nodes("a") %>% rvest::html_attr("href") %>% 
                grep("\\.tar\\.gz$", ., value = TRUE)

# Extract the exact full names of the .tar.gz files to be downloaded
exact_files <- tar_gz_files[grepl(paste0("^(", paste(required_packages, collapse = "|"), ")_.*\\.tar\\.gz$"), basename(tar_gz_files))]

# Start a loop over the list of exact full names of .tar.gz files to download all the files
for (file in exact_files) {
  #print(paste0(url, file))
  download.file(paste0(url, file), destfile = file)
}

# Use a vector-based syntax to install all the downloaded packages
install.packages(exact_files, repos = NULL, type = "source", dependencies = TRUE)
# Use remotes::install_local to install all the downloaded packages
#for (file in exact_files) {
#  remotes::install_local(file, dependencies = TRUE)
#}

```


# Run the below once to install more packages
```{r}

# Load necessary libraries
library(rvest) 
library(magrittr) 

required_packages <- c()
tar_gz_files <- c()
exact_files <- c()
# Save the required packages into a vector of strings
required_packages <- c(
  "bit64", "cachem", "ids", "memoise", "scales",
                       "tinytex", "bit64", "systemfonts", "clipr", "crayon", 
                       "tzdb", "cellranger", "data.table", "tidyselect",
                       "rematch2", "prettyunits", "readr", "digest", "timechange", "lubridate", 
                       "ggplot2", "tidyverse",
                       "htmltools", "svglite", "kableExtra"
                       )


# Collect the list of .tar.gz files from the webpage
url <- "https://cran.r-project.org/src/contrib/"
page <- rvest::read_html(url)
tar_gz_files <- page %>% rvest::html_nodes("a") %>% rvest::html_attr("href") %>% 
                grep("\\.tar\\.gz$", ., value = TRUE)

# Extract the exact full names of the .tar.gz files to be downloaded
exact_files <- tar_gz_files[grepl(paste0("^(", paste(required_packages, collapse = "|"), ")_.*\\.tar\\.gz$"), basename(tar_gz_files))]

# Start a loop over the list of exact full names of .tar.gz files to download all the files
for (file in exact_files) {
  #print(paste0(url, file))
  download.file(paste0(url, file), destfile = file)
}

# Use a vector-based syntax to install all the downloaded packages
install.packages(exact_files, repos = NULL, type = "source", dependencies = TRUE)
# Use remotes::install_local to install all the downloaded packages
#for (file in exact_files) {
#  remotes::install_local(file, dependencies = TRUE)
#}

```





#================================================================
















# Install Ubuntu packages harfbuzz and libfribidi
# harfbuzz is primarily a text shaping library used for rendering text
# fribidi is a library that provides support for the Unicode Bidirectional Algorithm (Bidi)
system("sudo apt-get install -y libharfbuzz-dev")
system("sudo apt-get install -y libfribidi-dev")
system("sudo apt-get install libfreetype6-dev")
# To find the installed location
system("dpkg-query -L libharfbuzz-dev")
system("dpkg-query -L libharfbuzz-dev")
system("dpkg-query -L libfreetype6-dev")

# Run the below once to install more packages
```{r}

# Load necessary libraries
library(rvest) 
library(magrittr) 

required_packages <- c()
tar_gz_files <- c()
exact_files <- c()
# Save the required packages into a vector of strings
required_packages <- c(
  "fontawesome", "jquerylib", 
  "hms", "progress", "bslib", "rmarkdown", "vroom", #"fs", 
  "textshaping", "gargle", "conflicted", #"dplyr", "ggplot2", 
  "dtplyr", "forcats",  
                       )


# Collect the list of .tar.gz files from the webpage
url <- "https://cran.r-project.org/src/contrib/"
page <- rvest::read_html(url)
tar_gz_files <- page %>% rvest::html_nodes("a") %>% rvest::html_attr("href") %>% 
                grep("\\.tar\\.gz$", ., value = TRUE)

# Extract the exact full names of the .tar.gz files to be downloaded
exact_files <- tar_gz_files[grepl(paste0("^(", paste(required_packages, collapse = "|"), ")_.*\\.tar\\.gz$"), basename(tar_gz_files))]

# Start a loop over the list of exact full names of .tar.gz files to download all the files
for (file in exact_files) {
  #print(paste0(url, file))
  download.file(paste0(url, file), destfile = file)
}

# Use a vector-based syntax to install all the downloaded packages
install.packages(exact_files, repos = NULL, type = "source", dependencies = TRUE)
# Use remotes::install_local to install all the downloaded packages
#for (file in exact_files) {
#  remotes::install_local(file, dependencies = TRUE)
#}
```


# Run the below once to install even more packages
```{r}
# Load necessary libraries
library(rvest) 
library(magrittr) 

required_packages <- c()
tar_gz_files <- c()
exact_files <- c()
# Save the required packages into a vector of strings
required_packages <- c(
  "googledrive", "googlesheets4", "haven", "readxl", "rstudioapi", "rlang",  
  "lazyeval", "languageserver", "rstudioapi", "dbplyr", "reprex", "backports", "broom", "modelr", "ragg"
                       )


# Collect the list of .tar.gz files from the webpage 
url <- "https://cran.r-project.org/src/contrib/"
page <- read_html(url)
tar_gz_files <- page %>% html_nodes("a") %>% html_attr("href") %>% 
                grep("\\.tar\\.gz$", ., value = TRUE)

# Extract the exact full names of the .tar.gz files to be downloaded
exact_files <- tar_gz_files[grepl(paste0("^(", paste(required_packages, collapse = "|"), ")_.*\\.tar\\.gz$"), basename(tar_gz_files))]

# Start a loop over the list of exact full names of .tar.gz files to download all the files
for (file in exact_files) {
  #print(paste0(url, file))
  download.file(paste0(url, file), destfile = file)
}

# Use a vector-based syntax to install all the downloaded packages
install.packages(exact_files, repos = NULL, type = "source", dependencies = TRUE)
# Use remotes::install_local to install all the downloaded packages
#for (file in exact_files) {
#  remotes::install_local(file, dependencies = TRUE)
#}

```


#export LD_LIBRARY_PATH=/workspaces/BBM104/R_Library:$LD_LIBRARY_PATH
#source ~/.bashrc
```{r}
#Sys.getenv("LD_LIBRARY_PATH")
Sys.setenv(LD_LIBRARY_PATH = paste("/workspaces/BBM104/R_Library", Sys.getenv("LD_LIBRARY_PATH"), sep = ":"))
```

```{r}

install.packages("tidyverse")#, dependencies = TRUE)
install.packages("kableExtra")#, dependencies = TRUE)
```


