---
title: "did - a package for difference-in-differences analysis with multiple time periods"
output: html_notebook
---


# Load required libraries

```{r}
library(did)
library(ggpubr)
library(BMisc)

library(dplyr)
library(tidyr)
library(readr)
library(gridExtra)
library(ggplot2) 
```


# Data preparation

- Load ESG data from Provider_B
- Apply log transformation to total emission variable
- Define new variables for DiD analysis
  - `YearMonth`: The year-month of an observation
  - `repealCPP`: The year-month when Trump repealed the Clean Power Plan (CPP)
  - `withdrawParis`: The year-month when Trump withdrew from the Paris Agreement
- Confine to the months in year 2017

```{r}

load("ESG_data_new.RData")
ESG_data_scope <- ESG_data_new %>% 
  mutate(
    scope = scope_1 + scope_2 + scope_3,  # Sum of Scope 1, 2, and 3 emissions
    lscope = log(scope + 1),  # Log transformation of scope_1 variable
    lscope_decile = ntile(lscope, 10),  # Divide lscope into 10 deciles for later analysis
    date = as.numeric(gsub("-", "", date)),  # Convert date in character type to numeric  
    YearMonth = as.numeric(substr(date, 1, 6)),  # YearMonth of an observation
    #========================================================================================
    repealCPP = 201703,  # YearMonth of 20170328 with Trump Repeal of Clean Power Plan (CPP)
    withdrawParis = 201706,  # YearMonth of 20170601 with Trump Withdrawal from Paris Agreement
    #========================================================================================
    firm_size = log(at),
    p2b = prcc_f / ceq,     # price to book ratio
    leverage_ratio = (dltt + dlc) / ceq,
    ) %>% 
  filter(!is.na(lscope)) %>%  #    retain only rows with non-missing values of lscope
  group_by(instrument) %>% 
    arrange(date) %>%
    # fill all missing values with the last available value for the range of columns GVKEY:last_col()
    fill(GVKEY:last_col(), .direction = "downup") %>%  
  ungroup() %>% 
  select(GVKEY, instrument, lscope_decile, lscope, YearMonth, repealCPP, withdrawParis, everything()) %>% 
  filter(!is.na(GVKEY)) %>%  #    GVKEY is the unique identifier for a company
  filter(date >= 20170101 & date < 20171231)  
  # 20161108: Trump was elected as the US President
  # 20170328: Trump Repeal of Clean Power Plan (CPP)
  # 20170601: Trump Withdrawal from Paris Agreement
  # 20201108: Biden was elected as the US President

```


# Set the policy change event
# Set the upper and lower limits of the range of lscope used for defining the treatment group

  - Units with lscope outside the range are used as the control group
  - Assumption: 
    - Companies with lscope at the two tails are likely to be constrained by structural factors (e.g., moral commitment or fundamental nature of a business) and hence unlikely to be influenced by any policy change
    
```{r}

#Event = "repealCPP"
Event = "withdrawParis"

upperlim = quantile(ESG_data_scope$lscope, 0.75) 
lowerlim = quantile(ESG_data_scope$lscope, 0.25)

```


# Descriptive information about the data

```{r}

#Summary statistics of date and lscope
cat("Summary of ESG_data_scope variables \n")
cat("\ndate: \n")
summary(ESG_data_scope$date)
cat("\nlog(scope): \n")
summary(ESG_data_scope$lscope)

#Summary statistics of ESG_data_scope
#summary(ESG_data_scope)


# Distribution of scope (before log transformation)
ESG_data_scope %>% 
  group_by(source) %>% 
  ggplot(aes(x = scope, fill = source)) + geom_density(alpha = 0.5)

# Distribution of log(scope) 
ESG_data_scope %>% 
  group_by(source) %>% 
  ggplot(aes(x = lscope, fill = source)) + 
    geom_vline(xintercept = upperlim, linetype = "dashed", color = "blue") +
    geom_text(x = (upperlim - 0.45), y = 0.09, label = sprintf("%.2f", upperlim), color = "blue") + 
    geom_vline(xintercept = lowerlim, linetype = "dashed", color = "blue") +
    geom_text(x = (lowerlim - 0.45), y = 0.09, label = sprintf("%.2f", lowerlim), color = "blue") + 
    geom_density(alpha = 0.5)

```


# Difference-in-Differences (DiD) analysis

- The `did` package contains tools for computing average treatment effect parameters in a DiD setup allowing for

  - Variation in treatment timing (i.e., units can become treated at different points in time)

- The `ESG_data_scope` dataset prepared earlier contains 4 years of monthly data during the period of the first Trump administration (November 2016 to October 2020). The important variables are: 

  - **lscope**: The log value of Scope 1 emissions as the `outcome` variable in DiD analysis
  
  - **YearMonth**: The year-month of an observation as the `time period` variable (integer) in DiD analysis
  
  - **first.treat**: The first time period when a unit is treated (e.g., when the direct greenhouse gas emission of a company is influenced by a policy change). It is the `group` variable in DiD analysis that defines the treatment timing. 
    - Set `first.treat = 0` for units in the **control group**, which are never treated
    - In this example, **green** companies (with `lscope <= LogThreshold`) are used as the control group (assumed to be unaffected by a policy change)
  
  - **GVKEY**:  The GVKEY of a company as the `id name` variable in DiD analysis, i.e., the individual (cross-sectional unit) identifier, which must be numeric as required by `did`. 
  
- The main parameters estimated by `did` are **group-time average treatment effects**, which are the average treatment effect for a particular group. 


# Estimate the group-time average treatment effects using the `att_gt()` function

- Set first.treat = withdrawParis

```{r}

# Set first.treat to withdrawParis
ESG_data_scope <- ESG_data_scope %>% 
  mutate(
    first.treat = ifelse(lscope >= lowerlim & lscope <= upperlim, 0, !!sym(Event))  # Define the first.treat variable
    )

out <- att_gt(
  yname = "lscope",
  tname = "YearMonth",
  gname = "first.treat",
  idname = "GVKEY",
  xformla = ~ firm_size + p2b + leverage_ratio,  # Control variables
#  xformla = ~ 1,  # No control variables
  data = ESG_data_scope     
)

# To see the estimates of the group-time average treatment effects and their standard errors
summary(out)

```


# Plot the group-time average treatment effects with the **ggdid** command

- The red dots in the plot are **pre-treatment** group-time average treatment effects. They are provided with 95\% simultaneous confidence intervals. These are the estimates that can be interpreted as **a pre-test of the parallel trends assumption**. 

- The blue dots are **post-treatment** group-time average treatment effects. Under the parallel trends assumption, these can be interpreted as **policy effects** -- here the effect of increased emissions due to the withdrawal from the Paris Agreement.

```{r, fig.width=8, fig.height=10, fig.align='center', out.width="90%", dpi = 200}

ggdid(out, ylim = c(-.25, .1))

```


# Overall Effect of Participating in the Treatment

```{r}

overall_effect <- aggte(out, type = "simple")
summary(overall_effect)

```
