---
title: "Dieselgate"
output: html_notebook
---

# Load required packages

```{r}
library(erer)  # package erer: Empirical Research in Economics with R
# erer::evReturn() is a function for event study analysis
library(tidyquant)  # package for fetching stock data from Yahoo Finance.
library(dplyr)
library(readr)
library(tidyr)
```


# define the event date and the window from which we want to fetch the data of the German auto companies.

```{r}

EventDate = 20150918    # The US-EPA announced VW's fraud publicly on 18.09.2015

startDate = "2013-01-01"   
endDate = "2015-12-31"

```


# focus on three motor manufacturers in Germany, namely

- VW Group
  - VW
  - Porsche
- BMW


# fetch the stock data from Yahoo Finance

```{r}

# Stock Data
firmSymbols <- c("VOW.DE", "PAH3.DE", "BMW.DE")
firmNames <- c("VW preferred", "Porsche Automobil Hld", "BMW")
firmSymbols %>% 
  tidyquant::tq_get(from = startDate, to = endDate) %>% 
  dplyr::mutate(date = as.numeric(format(date, "%Y%m%d"))) -> firmData

# Note: The date is not regular because there is no trading on weekends and holidays. Therefore, erer::evReturn() needs date to be represented by a number, not in a date format.

for (firm in firmSymbols) {
  knitr::kable(head(firmData %>% filter(firm == symbol)), pad=10) %>% print()
}

```


# choose the DAX as the reference market index

```{r}

# Index Data
indexSymbol <- c("^GDAXI")
indexName <- c("DAX")
indexSymbol %>% 
  tidyquant::tq_get(from = startDate, to = endDate) %>%  
  dplyr::mutate(date = as.numeric(format(date, "%Y%m%d"))) -> indexData

indexData$symbol <- "DAX"
knitr::kable(head(indexData), pad=10)

```

# Merge stock and index data after saving them as .csv files 

```{r}

# Stock data files for firms and market
firmData %>% 
  dplyr::select(symbol, date, adjusted) %>% 
  readr::write_delim(file      = "02_firmDataPrice.csv", 
                     delim     = ";", 
                     col_names = F)

indexData %>% 
  dplyr::select(symbol, date, adjusted) %>% 
  readr::write_delim(file      = "03_marketDataPrice.csv", 
                     delim     = ";", 
                     col_names = F)

# Merge stock and index data
evData <- indexData %>%  
  rename(MktIndex = adjusted) %>%
  select(date, MktIndex) %>% 
  right_join(firmData, by="date") %>% 
  select(-c(open, high, low, close)) %>%   # Remove price columns `open, high, low, close`
  # The above retains the adjusted price, which is the closing price adjusted for splits and dividends
  arrange(symbol, date)

summary(evData)

```


# Clean data: MktIndex has missing value on 2015-12-25, which is a public holiday!

```{r}

evData_is.na <- evData %>% 
  filter(is.na(MktIndex))

evData_xmas <- evData %>% 
  filter(date == 20151225)

evData_0vol <- evData %>% 
  filter(volume == 0) 

# Verify if the different data cleaning strategies yield the same data
identical(evData_is.na, evData_xmas)
identical(evData_is.na, evData_0vol)

# Review why the data cleaning strategies yield different data
View(evData_0vol)

# Ask Grok: https://grok.com
#   What happened to the stocks of BMW and VOW on 2014-03-18? They have zero trading volume.

# Finalize the data cleaning strategy
evData_cleaned <- evData %>% 
  filter(!is.na(MktIndex))   # ! (or != ) is the negation of a condition

```


# Housekeeping: Remove dataframe objects no longer needed, garbage collect, and restart R session

```{r}

# Remove dataframe objects no longer needed
rm(list = setdiff(ls()[sapply(ls(), function(x) is.data.frame(get(x)))], "evData_cleaned"))

# Garbage collection to regain leaked memory
gc()

# Restart R without removing the environment (only works on Posit Cloud)
#rstudioapi::restartSession()   

```


# Prepare the data for the event study analysis  
```{r}

evData_final <- evData_cleaned %>% 
  # arrange(symbol, date) %>%                  # For explaining the importance of group_by() operations
  # mutate(lag_adjusted = lag(adjusted)) %>%   # For explaining the importance of group_by() operations
  group_by(symbol) %>%  # For panel date, must group by each stock to calculate returns for each stock
    arrange(date) %>%   # Make sure date is in ascending order before applying the function lag()
    mutate(
      ret = (adjusted/lag(adjusted)) - 1,          # raw stock return
      MktIndexRet = (MktIndex/lag(MktIndex)) - 1,  # market index return
      ) %>%
    filter(!is.na(ret)) %>%  # keep only rows with non-missing ret_mkt 
    # mutate(
    #   t = row_number(),  # create t to indicate the time sequence as required by some event study packages
    #   ) %>%
  ungroup() %>%   # Good practice to ungroup() after operations requiring group_by() are done
  arrange(symbol, date) %>% 
  mutate(
    ret_mkt = ret - MktIndexRet,  # market-adjusted stock return
    # log_vol = log(volume + 1),     # define logVol as a control var. ; add 1 to avoid log(0) = -Inf
    # id = as.numeric(factor(symbol)),  # convert symbol to a number as required by some event study packages
    # eventtime = EventDate,  
    # eventON = ifelse(date >= eventtime, 1, 0),  # indicate whether the event has occurred
  ) %>% 
  select(symbol, 
         # id, eventtime, t, eventON, 
         date, ret_mkt, 
         # log_vol, 
         everything()) # organize the columns  

summary(evData_final)

```


#============================================================================================

# The parameters for this Event Study are:

  - Estimation window of the market model: 250 days
  - Event window: -10 to 10 days
  - Event date: 18 September 2015   (The date on which US-EPA announced VW's fraud publicly)

# The three motor manufacturers in Germany considered here:

- VW Group
  - VW
  - Porsche
- BMW


# Event Study analysis by erer::evReturn()
### BMW

```{r}

# Prepare data for event study analysis by erer::evReturn()
data_evReturn <- evData_final %>%  
  select(symbol, date, MktIndexRet, ret) %>%  
  tidyr::spread(key=symbol, value=ret)  # spread() reorganizes the data in the format required by erer::evReturn()
# Note: The raw return (ret) of each stock is used here because erer::evReturn() calculates the abnormal return internally from the normal return estimated with a market model based on MktIndexRet specified in the function call below.

# event analysis for multiple firms and one event window
hh0 <- evReturn(
  y = data_evReturn,        # data for the event study analysis
  firm = c("BMW.DE"),       # raw stock return columns used in the analysis 
  y.date = "date",          # date column in the data
  index = "MktIndexRet",    # market index return column in the data
  est.win = 250,            # Estimation window for the market model: 250 trading days ~ 1 calendar year
  event.date = EventDate,   # date of the event
  event.win = 10            # Event window: -10 to 10 days around the event date
  )   
hh0; plot(hh0)

```

# Event Study analysis by erer::evReturn()
### VW Group: VW and Porsche

```{r}

# event analysis for multiple firms and one event window
hh <- evReturn(
  y = data_evReturn,             # data for the event study analysis
  firm = c("VOW.DE", "PAH3.DE"), # raw stock return columns used in the analysis 
  y.date = "date",               # date column in the data
  index = "MktIndexRet",         # market index return column in the data
  est.win = 250,                 # Estimation window for the market model: 250 trading days ~ 1 calendar year
  event.date = EventDate,        # date of the event
  event.win = 10                 # Event window: -10 to 10 days around the event date
  )
hh; plot(hh)

#===============================================================================================
# Details about the analysis output hh:
# 
# Ait.FirmX = hh$abr$Ait.FirmX = abnormal return (AR) of FirmX for period t in the event window
# HNt = The average AR across firms for period t in the event window
# CiT.FirmX = hh$abc$Cit.FirmX = sum(hh$abr$Ait.FirmX) 
#   = The cumulative abnormal return (CAR) of FirmX, where FirmX = {VOW.DE, PAH3.DE}
# GNT = The average CAR across firms

```


