---
title: "GreenPerformance"
output: html_document
date: "2025-01-08"
---


# Load libraries and data
```{r setup, include=FALSE}

repo_path <- normalizePath(getwd())
# Add the R-library directory to the search path 
.libPaths(c(file.path(repo_path, "R_Library"), .libPaths()))

library(tidyverse)
library(lubridate)
library(kableExtra)
load(file.path(repo_path, "/Session06/ESG_data.RData"))

```


# ? 
```{r}
q <- 0.5
ESG_data |> 
  filter(year(date) > 2002, year(date) < 2024) |>
  filter(source == "Provider_B") |>
  group_by(date) |>                # This means that all operations will be run date by date, separately
  mutate(type = if_else(esg_metric > quantile(esg_metric, q, na.rm = T), # This creates the sorts...
                        "Green",                                         # ...Green if high ESG...
                        "Brown")) |>                                     # ...Brown if not
  select(name, date, close, esg_metric, type)                            # Select a few columns

```

#q: What does the R code chunk just above do? Please explain the logical flow intuitively without showing each line of code in your reply.
#a: The code filters the data to keep only the years between 2002 and 2024 and the data from Provider_B. It then groups the data by date and creates a new column called type that is Green if the esg_metric is greater than the 50th percentile and Brown otherwise. Finally, it selects only the name, date, close, esg_metric, and type columns.

#q: How should the heading of the R code chunk above be called?
#a: Filtering and sorting ESG data by date and source


#q: What does the next R code chunk do? Please explain the logical flow intuitively without showing each line of code in your reply.
#a: The code groups the data by firm and computes the return of each stock by dividing the close price by the previous close price and subtracting 1. It then removes the grouping and filters out the returns that are greater than 3.

# ? 
```{r}
q <- 0.5
ESG_data |> 
  filter(year(date) > 2002, year(date) < 2024) |>
  filter(source == "Provider_B") |>
  group_by(date) |>                # This means that all operations will be run date by date, separately
  mutate(type = if_else(esg_metric > quantile(esg_metric, q, na.rm = T), # This creates the sorts...
                        "Green",                                         # ...Green if high ESG...
                        "Brown")) |>                                     # ...Brown if not
  ungroup() |>
  group_by(name) |>                                                      # Now we group by firm
  mutate(return = close / lag(close) - 1) |>                             # Here we compute the return
  filter(return < 3) |>                                                  # Remove crazy returns
  select(name, date, close, esg_metric, type, return)

```

Note: A different answer was given (see below) when the R code chunk was selected by mouse and the question is asked in the chatbox panel on the right side of the screen.

#Q: What does the selected R code chunk do? Please explain the logical flow intuitively without showing each line of code in your reply.

#A: The selected R code chunk filters the data to keep only the years between 2002 and 2024 and the data from Provider_B. It then groups the data by date and creates a new column called type that is Green if the esg_metric is greater than the 50th percentile and Brown otherwise. After that, it groups the data by firm and computes the return of each stock by dividing the close price by the previous close price and subtracting 1. It then filters out the returns that are greater than 3 and selects only the name, date, close, esg_metric, type, and return columns.


# ? 
```{r}
ESG_data <- ESG_data |>  
  group_by(name) |>                                           # Now we group by firm
  mutate(return = close / lag(close) - 1) |>                  # Here we compute the return             
  ungroup() 
```


# ? 
```{r}
q <- 0.5
ESG_data |> 
  filter(year(date) > 2002, year(date) < 2024) |>
  filter(source == "Provider_B", is.finite(esg_metric)) |>    # Keeps non missing ESG fields
  group_by(date) |>                    # All operations will be run date by date, separately
  mutate(type = if_else(esg_metric > quantile(esg_metric, q), # This creates the sorts...
                        "Green",                              # ...Green if high ESG...
                        "Brown")) |>                          # ...Brown if not
  ungroup() |>
  filter(return < 3) |>                                       # Remove crazy returns
  group_by(type) |>
  summarise(avg_return = mean(return, na.rm = T))  |>
  kableExtra::kable(caption = 'ESG metric and portfolio performance (q = 0.5) - Provider B')
```


# ? 
```{r}
q <- 0.5
ESG_data |> 
  filter(year(date) > 2002, year(date) < 2024) |>
  filter(source == "Provider_A", is.finite(esg_metric)) |>    # Keeps non missing ESG fields
  group_by(date) |>                    # All operations will be run date by date, separately
  mutate(type = if_else(esg_metric < quantile(esg_metric, q), # This creates the sorts...
                        "Green",                              # ...Green if high ESG...
                        "Brown")) |>                          # ...Brown if not
  ungroup() |>
  filter(return < 2) |>                                       # Remove crazy returns!
  group_by(type) |>
  summarise(avg_return = mean(return*12, na.rm = T)) |>
  kableExtra::kable(caption = 'ESG metric and portfolio performance (q = 0.5) - Provider A')
```


# ? 
```{r}
q <- 0.5
ESG_data |> 
  filter(year(date) > 2002, year(date) < 2024) |>
  mutate(intensity = scope_3 / market_cap) |>
  filter(source == "Provider_A", is.finite(intensity)) |>     # Keeps non missing ESG fields
  group_by(date) |>                    # All operations will be run date by date, separately
  mutate(type = if_else(intensity < quantile(intensity, q),   # This creates the sorts...
                        "Green",                              # ...Green if high ESG...
                        "Brown")) |>                          # ...Brown if not
  ungroup() |>
  filter(return < 2) |>                                       # Remove crazy returns
  group_by(type) |>
  summarise(avg_return = mean(return*12, na.rm = T) * 12)  |>    # Annualize
  kableExtra::kable(caption = 'Scope 3 intensity and portfolio performance (q = 0.5)')
```


# ? 
```{r}
q <- 0.2
ESG_data |> 
  filter(year(date) > 2002, year(date) < 2024) |>
  filter(source == "Provider_B") |>
  group_by(date) |>                # This means that all operations will be run date by date, separately
  mutate(type = if_else(esg_metric > quantile(esg_metric, 1-q, na.rm = T),  # This creates the sorts...
                        "Green",                                            # Green if high
                        if_else(esg_metric < quantile(esg_metric, q, na.rm = T),
                                "Brown",                                 # ...Brown if low...
                                "Grey"))) |>                             # ... Grey otherwise
  ungroup() |>
  filter(is.finite(esg_metric), return < 3) |>
  group_by(type) |>
  summarize(avg_return = mean(return*12, na.rm = T))  |>
  kableExtra::kable(caption = 'ESG metric and portfolio performance (q = 0.2)')
```


# ? 
```{r}
q <- 0.2
ESG_data |> 
  filter(year(date) > 2002, year(date) < 2024) |>
  mutate(intensity = scope_3 / market_cap) |>
  filter(source == "Provider_A", is.finite(intensity)) |>     # Keeps non missing ESG fields
  group_by(date) |>                    # All operations will be run date by date, separately
  mutate(type = if_else(intensity < quantile(intensity, q),   # This creates the sorts...
                        "Green",                              # ...Green if high ESG...
                        if_else(intensity > quantile(intensity, 1-q),
                                "Brown",
                                "Grey"))) |>                          # ...Brown if not
  ungroup() |>
  group_by(name) |>                                           # Now we group by firm
  mutate(return = close / lag(close) - 1) |>                  # Here we compute the return             
  ungroup() |>
  filter(return < 2) |>
  group_by(type) |>
  summarise(avg_return = mean(return, na.rm = T) * 12) |>
  kableExtra::kable(caption = 'Scope 3 intensity and portfolio performance (q = 0.2)')
```

